Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-09-08 revision_cover_letter.tex
Typos corregidos

\item Reviewer 1 said: \textit{By the same reasoning, the orientation of
    bicelles reflect their size/anisotropy in the NMR time scale. It is not
    that ``it orient ifself'' as stated here: “Also, the membrane mimetic
    must orient itself in presence of an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a quadrupole splitting in a
  solution 2H-RMN spectrum”. Please rephrase that.}

@@

\item Reviewer 1 said: \textit{Fig. 9, what is the reason for the change in
    frequency (-100 Hz to + 100 Hz) observed with levoDOPA, in the acyl chain
    carbons 4-5?}\\
	Although a reduction in the quadrupolar splitting may be due to a solvation of the charged polar heads from the zwitterionic Levodopa, in this case the effect is small and within margin of error, which is why we concluded that the effects of this aminoacid on the bilayer are minor to negligible.

\item Reviewer 1 said: \textit{By the same reasoning, the orientation of bicelles reflect their size / anisotropy in the NMR time scale. It is not that “it orient ifself” as stated here: “Also, the membrane mimetic must orient itself in presence of an external magnetic field. This is so the deuterated probes in the mimetic can produce a quadrupole splitting in a solution 2H-RMN spectrum”. Please rephrase that.}
We agree, the preferred orientation of the bicelle is the result of the anisotropy of its magnetic susceptibility. The sentence has been modified to reflect that.

>>>>

@@

\item Reviewer 1 said: \textit{Fig. 9, what is the reason for the change in
    frequency (-100 Hz to + 100 Hz) observed with levoDOPA, in the acyl chain
    carbons 4-5?}\\
	In this case the effect on the quadrupolar splitting is small and within margin of error, which is why we concluded that the effects of this aminoacid on the bilayer are minor to negligible.

\item Reviewer 1 said: \textit{By the same reasoning, the orientation of bicelles reflect their size / anisotropy in the NMR time scale. It is not that “it orient ifself” as stated here: “Also, the membrane mimetic must orient itself in presence of an external magnetic field. This is so the deuterated probes in the mimetic can produce a quadrupole splitting in a solution 2H-RMN spectrum”. Please rephrase that.}
We agree, the preferred orientation of the bicelle is the result of the anisotropy of its diamagnetic susceptibility. The sentence has been modified to reflect that.
